Timeliness of security updates for Android

### 2015-03-16 security_scoring.tex
Minor fixes
Add paragraph about distribution of updates to models

\begin{equation}
\mathrm{score} = f\times 4 + u \times 3 + \frac{2}{1+e^m} \times 3 \label{eq:score}
\end{equation}

@@

>>>>

\begin{equation}
\mathrm{score} = 4 \cdot f + 3 \cdot u + 3 \cdot \frac{2}{1+e^m} \label{eq:score}
\end{equation}

@@

If update delays are due to the delay in manufacturers providing the update rather than in operators in supplying the update and users installing the update we would expect the update behaviour of devices with the same device model to be similar.
We found that within \daModelHalfDeployment\ days of the first observation of a new version on a device, half of all devices of that model have the new version (or a higher version) installed, and within \daModelFullDeployment\ days \daFullDeployedAt\ of devices have the new version (or a higher version).
There is a variation between device models, with the update being distributed to most devices quickly and others having a much slower roll out but since some do update quickly the bottleneck is unlikely to be with the user.
